An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-11-03 mixedwindow.tex
Tweak notation

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In the 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
the 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimators of $\beta_0$ do not converge to $\beta_0$.

@@

Finally, we define some notation for the \oos\ statistic. The
adjusted OOS loss for each alternative model and a hypothetical value
of $\beta$ is denoted by
\begin{equation}
  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
\end{equation}
and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
Also define
\begin{align*}
  \fh_t &= f_t(\bh),
  &\fb(\beta) &= \oavg{t} f_t(\beta),
  &\text{and}&
  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
\end{align*}
with $P = T - R$. Also define $\beta_0$ to be the pseudotrue value of
$\beta$ that minimizes the MSE of the benchmark model,
\begin{equation*}
  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
\end{equation*}
and let $\Sigma$ be the asymptotic variance of $\fb$, $\Sigma
= \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
The next assumption ensures that $\Sigma$ is positive definite.
\begin{asmp}\label{a4}%
  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
\end{asmp}

@@

\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}

Null hypothesis: $y_{t+1} - x_t'\beta_0$ is an MDS with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

@@

Define the variables
$g_t(\beta) = \Fh \Bh x_t(y_{t+1} - x_t'\beta)$,
$\gh_t = g_t(\bh_t)$, and $\gb = \oavg{t} \gh_t$.

>>>>

\citet{ClW:06,ClW:07} develop a test of whether $\ep_{t+1}$ is
an \mds. In the 2006 paper, Clark and West assume that the
coefficients on the benchmark model, $\btrue$, are zero under the null, making
$\ep_{t+1}$ observed directly. This restriction is relaxed in
the 2007 paper, where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\eph_{t+1}$, replace $\ep_{t+1}$ in the \oos\
test statistic. Unfortunately, $\eph_{t+1}$ is not an
\mds\ even when $\ep_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations. Since the window length is finite,
the estimators of $\btrue$ do not converge to $\btrue$.

@@

Finally, we define some notation for the \oos\ statistic. The
adjusted OOS loss for each alternative model and a hypothetical value
of $\beta$ is denoted by
\begin{equation}
  f_{jt}(\beta) = (y_{t+1} - x_t'\beta)^2
  - (y_{t+1} - \yh_{j,t+1})^2 + (x_t'\beta - \yh_{j,t+1})^2
\end{equation}
and $f_t(\beta)$ denotes the vector $(f_{1t}(\beta),\dots,f_{Jt}(\beta))$.
Also define
\begin{align*}
  \fh_t &= f_t(\bh),
  &\fb(\beta) &= \oavg{t} f_t(\beta),
  &\text{and}&
  &\fb &= \tfrac1P \sum_{t=R+1}^{T} \fh_t
\end{align*}
with $P = T - R$, and let $\Sigma$ be the asymptotic variance of
$\fb$, $\Sigma = \lim_{T \to \infty} \var(\sqrt{P} \fb)$.
Also define $\btrue$ to be the pseudotrue value of
$\beta$ that minimizes the MSE of the benchmark model,
\begin{equation*}
  \btrue = \plim \Big( \sum_{t=1}^T x_t x_t' \Big)^{-1} \sum_{t=1}^T x_t y_{t+1},
\end{equation*}
and define $f_t = f_t(\btrue)$ and $\fb^* = \fb(\btrue)$.
The next assumption ensures that $\Sigma$ is positive definite.
\begin{asmp}\label{a4}%
  The asymptotic variance of $\fb$, $\Sigma$, is positive definite.
\end{asmp}

@@

\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}
In Theorem~\ref{res:1}, define the variables
$\gh_t = \Fh \Bh x_t(y_{t+1} - x_t'\bh_t)$,
$g_t = F B x_t (y_{t+1} - x_t'\btrue)$,
$\gb = \oavg{t} \gh_t$, and $\gb^* = \oavg{t} g_t$.

Null hypothesis: $y_{t+1} - x_t'\btrue$ is an MDS with respect to
\begin{equation*}
  \Fs = \sigma((x_t, y_t, z_t), (x_{t-1}, y_{t-1}, z_{t-1}), \dots).
\end{equation*}

@@
